RDF Validation of Metadata \\ on Person-Level and Aggregated Data

### 2015-03-02 paper/paper7/paper7.tex
4.2

\textbf{Variables.}

- variable does not have associated codes / categories

 (\emph{R-71: conditional properties}).
If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}).
%\footref{R-71-CONDITIONAL-PROPERTIES}

>>>>

\textbf{Variables.}
Each variable should have a variable representation (\emph{R-86: existential quantification}), which is either an (un)ordered code list or a union of XML Schema datatypes.
If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}) (\emph{R-71: conditional properties}).
%\footref{R-71-CONDITIONAL-PROPERTIES}
